---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# birdseyeview

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/birdseyeview)](https://CRAN.R-project.org/package=birdseyeview)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of birdseyeview is to make it easy to create the types of maps, plots, and tables used for community plans. This package is designed to use the [overedge package](https://elipousson.github.io/overedge/) and data packages like [mapbaltimore](https://elipousson.github.io/mapbaltimore/) or [bcpss](https://elipousson.github.io/bcpss/) to create reproducible maps and tables for a range of needs.

## Installation

You can install the development version of birdseyeview like so:

``` r
remotes::install_github("elipousson/birdseyeview")
```

## Example

```{r setup}
library(birdseyeview)
library(ggplot2)
library(sf)
```
