---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# birdseyeview

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/birdseyeview)](https://CRAN.R-project.org/package=birdseyeview)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of birdseyeview is to make it easy to create the types of maps, plots, and tables used for community plans.

This package was initially designed to use the [overedge package](https://elipousson.github.io/overedge/) and data packages like [mapbaltimore](https://elipousson.github.io/mapbaltimore/) or [bcpss](https://elipousson.github.io/bcpss/) to create reproducible maps and tables for a range of needs. The {overedge} package has since been superseded by sfext, getdata, and maplayer. maplayer incorporated most of the mapping functions creating for birdseyeview. These duplicative functions were removed from birdseyeview in Setember 2022.

## Installation

You can install the development version of birdseyeview like so:

``` r
remotes::install_github("elipousson/birdseyeview")
```

## Example

```{r setup}
library(birdseyeview)
library(getdata)
library(sfext)
library(maplayer)
```


### Make tables 

```{r gt_sf_rows}
parks <-
  getdata::get_location_data(
    data = "parks",
    package = "mapbaltimore"
  )

parks %>%
  dplyr::slice_head(n = 4) %>%
  dplyr:::select(name, address, park_district, acres, geometry) %>%
  dplyr::group_by(park_district) %>%
  gt::gt() %>%
  gt_sf_rows(fill = "forestgreen", color = "lightgreen", size = 6)
```

```{r tbl_photo_key, eval = FALSE}
park_photos <-
  getdata::get_flickr_photos(
    user_id = "baltimoreheritage",
    tags = "druidhillpark",
    img_size = "m",
    sort = "date-posted",
    per_page = 20
  )

park_photos[1:6, ] %>%
  dplyr::select(title, datetaken, image_height, image_width, image_url) %>%
  tbl_photo_key(photo_col = "image_url", orientation = "landscape", number = TRUE)
```

### Make maps

```{r}
library(ggplot2)
```


```{r layer_show_context}
ggplot() +
  maplayer::layer_location_context(
    data = parks[245, ],
    fill = "green",
    context = parks,
    context_params = list(fill = "forestgreen", color = "gray60", alpha = 1)
  )
```


```{r make_group_layers, eval=FALSE}
# make_group_layers has been dropped from birdseyeview but isn't available in maplayer yet
park_district_layers <-
  make_group_layers(
    data = parks %>% sf::st_centroid(),
    mapping = aes(color = name),
    groupname_col = "park_district"
  )

clifton_district <-
  getdata::get_location(
    type = "park_districts",
    package = "mapbaltimore",
    name = "Clifton"
  )

ggplot() +
  park_district_layers[[1]] +
  guides(color = "none") +
  layer_show_location(
    data = clifton_district
  ) +
  theme_void()
```
